**Urinary Vitamin D Binding Protein as a Potential Biomarker for Nephropathy in Patients at risk for Type 2 Diabetes**: The Prospective Metabolism and Islet Cell Evaluation (PROMISE) cohort study.

### 2017-02-17 doc/adaAbstract.Rmd
Replaced setup with functions and added sub char table

---
title: "ADA Abstract"
author: "Windy Wang"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

library(dplyr)

ds <- readRDS(file='../data/ds.Rds') %>% 
  dplyr::mutate(logUdbpRatio = log(udbpCrRatio)) %>% 
  dplyr::select(SID, VN, fVN, Age, ACR, eGFR, UDBP,
                acr_status, eGFR_status, UDBP_status, 
                udbpCrRatio, logUdbpRatio, 
                DM, dm_status)
  # dplyr::group_by(SID) %>% 
  # dplyr::filter(n() == 3) %>% 
  # dplyr::ungroup()

ds1 <- ds %>% 
  dplyr::filter(fVN == "Baseline")

source('../R/functions.r')
source("../R/gee.R")
source("../R/graphs.R")

@@

Subject characteristics across visit numbers
```{r subject characteristics}
table_subChar(ds1)

# check n
table(ds1$acr_status)

# 
# # check n of multiple variables
ds %>%
  dplyr::tbl_df() %>%
  dplyr::filter(VN == 3) %>%
  dplyr::select(VN, fVN, SID, Age, ACR, eGFR, UDBP) %>%
  tidyr::gather(Measure, Value, -SID) %>%
  na.omit() %>%
  dplyr::group_by(Measure) %>%
  dplyr::summarise(n = n())

Statististical tests
```{r stats}

## make sure that it is okay to do chi-square with longitudinal
## make sure the error term for anova is correct

summary(aov(Age ~ fVN + Error(SID/fVN), data=ds))

chisq.test(table(ds$Ethnicity, ds$fVN), correct = TRUE)

chisq.test(table(ds$Sex, ds$fVN), correct = TRUE)

summary(aov(BMI ~ fVN + Error(SID/fVN), data=ds))

summary(aov(Waist ~ fVN + Error(SID/fVN), data=ds))

summary(aov(eGFR ~ fVN + Error(SID/fVN), data=ds))

summary(aov(ACR ~ fVN + Error(SID/fVN), data=ds))

summary(aov(UrineCreatinine ~ fVN + Error(SID/fVN), data=ds))

summary(aov(UrineMicroalbumin ~ fVN + Error(SID/fVN), data=ds))

summary(aov(UDBP ~ fVN + Error(SID/fVN), data=ds))

summary(aov(Creatinine ~ fVN + Error(SID/fVN), data=ds))

summary(aov(VitaminD ~ fVN + Error(SID/fVN), data=ds))

summary(aov(PTH ~ fVN + Error(SID/fVN), data=ds))

summary(aov(ALT ~ fVN + Error(SID/fVN), data=ds))

summary(aov(Systolic ~ fVN + Error(SID/fVN), data=ds))

summary(aov(Diastolic ~ fVN + Error(SID/fVN), data=ds))

summary(aov(MeanArtPressure ~ fVN + Error(SID/fVN), data=ds))

summary(aov(Glucose0 ~ fVN + Error(SID/fVN), data=ds))

summary(aov(Glucose120 ~ fVN + Error(SID/fVN), data=ds))

chisq.test(table(ds$dm_status, ds$fVN), correct = TRUE)

# TukeyHSD(anova, which="fVN")
```

>>>>

---
title: "**Urinary Vitamin D Binding Protein as a Potential Biomarker for Nephropathy in Patients at risk for Type 2 Diabetes**: The Prospective Metabolism and Islet Cell Evaluation (PROMISE) cohort study."
author: "Wang WZN, Cole DEC, Johnston LW, Wong BYL, Fu L, Retnakaran R, Harris SB, Zinman B, Hanley AJ"
output: word_document:
          fig_caption: yes
          reference_docx: wordStyle.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, echo = FALSE, message = FALSE, warning = FALSE)
library(dplyr)
devtools::load_all()
load_data(update = TRUE)
set_options()
```

```{r dsSetup}
ds <- project_data

dsBase <- ds %>% 
  dplyr::filter(fVN == "Baseline")

dsComplete <- ds %>% 
  dplyr::group_by(SID) %>%
  dplyr::filter(n() == 3) %>%
  dplyr::ungroup()
```

```{r captionSetup}
## Include captions below using `captioner` package
figNums <- captioner::captioner(prefix = 'Figure')
supFigNums <- captioner::captioner(prefix = 'Supplementary Figure')
tabNums <- captioner::captioner(prefix = 'Table')
supTabNums <- captioner::captioner(prefix = 'Supplementary Table')
```

@@

Subject characteristics across visit numbers
```{r subject characteristics}

subCharTable <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "eGFR",
           "ACR",
           "UrineCreatinine",
           "UrineMicroalbumin",
           "UrinaryCalcium",
           "UDBP",
           "Creatinine",
           "VitaminD",
           "PTH",
           "ALT",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "Glucose0",
           "Glucose120",
           "dmStatus",
           "SmokeCigs"),
  strata = c("fVN"),
  data = ds,
  factorVars = c("Sex", "SmokeCigs")
) %>% 
  print(nonnormal = c("Glucose0",
                      "Glucose120",
                      "ALT",
                      "UDBP",
                      "ACR")) %>% 
  pander::pander()
```
